---
title: "Wei's Netflix Circle"
author: "Ella Ngo"
date: "2/1/2023"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE, warning=FALSE}
```

# Background

A brief data analyis of my boyfriend (Wei)'s Netflix watch history compared to his sister's, his parents', and his friend's.

Wei has always been into films, movies, shows, etc., so I aimed to put together a graph highlighting how much more things he watches on netflix on average than people in his circle.

I would like to thank my friend Taylor Blair, whose project on the difference in frequencies of watching Netflix between her sister and her inspired this project of mine.

# Loading Libraries and Data


```{r, warning=FALSE, error=FALSE, results="hide", message=FALSE}
library(tidyverse)
library(openair)
library(readr)
```

```{r message=FALSE}
wei_history <- read_csv("~/Desktop/R/NetflixViewingHistory.csv")
isa_history <- read_csv("~/Desktop/R/NetflixViewingHistory-2.csv")
parent_history <- read_csv("~/Desktop/R/ParentNetflixHistory.csv")
friend_history <- read_csv("~/Desktop/R/FriendNetflixHistory.csv")
```

---

# Data Prep

As can be seen above, the initial dataset contains only two variables. 

## Date fixing
```{r}
wei_history$Date <- as.Date(wei_history$Date,"%m/%d/%y")
isa_history$Date <- as.Date(isa_history$Date,"%m/%d/%y")
parent_history$Date <- as.Date(parent_history$Date,"%m/%d/%y")
friend_history$Date <- as.Date(friend_history$Date,"%m/%d/%y")
```


## Movie or TV series
```{r}
wei_history$type <- grepl(":", wei_history$Title)
wei_history$type <- wei_history$type %>%
  replace(wei_history$type==TRUE, "TV Series") %>%
  replace(wei_history$type==FALSE, "Movie")
isa_history$type <- grepl(":", isa_history$Title)
isa_history$type <- isa_history$type %>%
  replace(isa_history$type==TRUE, "TV Series") %>%
  replace(isa_history$type==FALSE, "Movie")
parent_history$type <- grepl(":", parent_history$Title)
parent_history$type <- parent_history$type %>%
  replace(parent_history$type==TRUE, "TV Series") %>%
  replace(parent_history$type==FALSE, "Movie")
friend_history$type <- grepl(":", friend_history$Title)
friend_history$type <- friend_history$type %>%
  replace(friend_history$type==TRUE, "TV Series") %>%
  replace(friend_history$type==FALSE, "Movie")
```

## Series, Season and episode

```{r, warning=FALSE, error=FALSE, results="hide"}
wei_history <- wei_history %>%
  separate(Title,
           c("Series", "Season", "Episode"),
           ": ")
isa_history <- isa_history %>%
  separate(Title,
           c("Series", "Season", "Episode"),
           ": ")
parent_history <- parent_history %>%
  separate(Title,
           c("Series", "Season", "Episode"),
           ": ")
friend_history <- friend_history %>%
  separate(Title,
           c("Series", "Season", "Episode"),
           ": ")
```


## Day of Week

```{r}
day_of_week <- function(x){
  return (weekdays(x))
}
days <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
wei_history$day <- sapply(wei_history$Date, day_of_week)
wei_history$day <- factor(wei_history$day, 
                         levels = days)
isa_history$day <- sapply(isa_history$Date, day_of_week)
isa_history$day <- factor(isa_history$day, 
                              levels = days)
parent_history$day <- sapply(parent_history$Date, day_of_week)
parent_history$day <- factor(parent_history$day, 
                         levels = days)
friend_history$day <- sapply(friend_history$Date, day_of_week)
friend_history$day <- factor(friend_history$day, 
                              levels = days)
```

## Outputted Tibble

```{r}
sample_n(wei_history, 4)
```

---

#Compare dataset

```{r}
wei_history$individual <- "Wei"
isa_history$individual <- "Isa"
friend_history$individual <- "Parent"
parent_history$individual <- "Friend"
merged <- rbind(wei_history, isa_history, parent_history, friend_history)
```

---

# Numerical analysis


## Binge Watching

Everyone has binged watched Netflix at some point during 2021, unfortunately :(. 

```{r}
```

---

# Graphical Analysis

```{r}
ggplot(merged, aes(x = day, fill=individual) ) +
  geom_bar(position = "dodge") +
  labs(title = "Wei's circle: Netflix Shows Watched by Day") +
  scale_fill_manual("Individual", values=c("#fdf2b8","#e88200", "#cb2800", "#34262b")) +
  xlab("Day of Week") +
  ylab("Number of Episodes Watched")
```

## A Calander of Events

2021 was a unique year, with Wei going to college in September, so it's weird that he *might* have watched more Netflix then....

```{r}
wei_history %>%
  group_by(Date) %>%
  summarise(count = n()) %>%
  rename(date=Date) %>%
  calendarPlot(pollutant = "count",
             year = 2021, main="Netflix Episodes watched in 2021")
isa_history %>%
  group_by(Date) %>%
  summarise(count = n()) %>%
  rename(date=Date) %>%
  calendarPlot(pollutant = "count",
              year = 2021,
              month = c(1:12))
parent_history %>%
  group_by(Date) %>%
  summarise(count = n()) %>%
  rename(date=Date) %>%
  calendarPlot(pollutant = "count",
             year = 2021,
             month = c(1:12))
friend_history %>%
  group_by(Date) %>%
  summarise(count = n()) %>%
  rename(date=Date) %>%
  calendarPlot(pollutant = "count",
              year = 2021,
              month = c(1:12))
```

